---
title: "DATA 607 Project 3"
author: "Jun Pan"
date: "October 18, 2018"
output: html_document
---

Project – Data Science Skills 
This is a project for your entire class section to work on together, since being able to work effectively on a virtual team is a key “soft skill” for data scientists.  Please note especially the requirement about making a presentation during our first meetup after the project is due. 
 
‘nycﬂights13’ DATABASE

Title Flights that Departed NYC in 2013 

Description Airline on-time data for all ﬂights departing NYC in 2013. Also includes useful 'metadata' on airlines, airports, weather, and planes. 

the database is availabe as a r package. 

the other source for this database includes:
URL http://github.com/hadley/nycflights13 

Source https://www.transtats.bts.gov/DL_SelectFields.asp?Table_ID=236

Format Data frame with columns 

year,month,day: Date of departure 

dep_time,arr_time: Actual departure and arrival times (format HHMM or HMM), local tz.

sched_dep_time,sched_arr_time: Scheduleddepartureandarrivaltimes(formatHHMMorHMM), local tz.

dep_delay,arr_delay: Departure and arrival delays, in minutes. Negative times represent early departures/arrivals.

hour,minute: Time of scheduled departure broken into hour and minutes.

carrier: Two letter carrier abbreviation. See airlines() to get name 

tailnum: Plane tail number 

ﬂight: Flight number 

origin,dest: Origin and destination, See airports() for additional metadata.

air_time: Amount of time spent in the air, in minutes 

distance: Distance between airports, in miles 

time_hour: Scheduled date and hour of the ﬂight as a POSIXct date. Along with origin, can be used to join ﬂights data to weather data.

```{r}
install.packages("nycﬂights13")
```
```{r}
library(nycflights13)
```


set working enviornment
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```


#Overview of database

```{r}
head(flights)
```
```{r}
tail(flights)
```

```{r}
dim(flights)
```
the dataframe has 336776 rows and 19 columns.
```{r}
summary(flights)
```

